%-------------------------
% Cover Letter in LaTeX
% Matching style with main.tex CV
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Hassan Refaat} \\ \vspace{1pt}
    \small Cairo, Egypt $|$ +20 1221736193 $|$ \href{mailto:hassan.refaat.dev@gmail.com}{\underline{hassan.refaat.dev@gmail.com}} $|$
    \href{https://linkedin.com/in/refaatcrafts}{\underline{linkedin}} $|$
    \href{https://github.com/refaatcrafts}{\underline{github}} $|$
    \href{https://refaatcrafts.space}{\underline{blog}}
\end{center}

\vspace{20pt}

%----------DATE----------
% TODO: Replace with application date
\noindent
{DATE}

\vspace{15pt}

%----------RECIPIENT----------
% TODO: Replace with hiring manager name if known, otherwise use title
\noindent
{HIRING\_MANAGER} \\
{COMPANY\_NAME} \\

\vspace{15pt}

%----------SALUTATION----------
\noindent
Dear Hiring Manager,

\vspace{10pt}

%----------OPENING PARAGRAPH (THE HOOK)----------
% TODO: Customize this paragraph for each application
% - Reference why you're excited about THIS specific company
% - Mention the specific role you're applying for
% - Quick value proposition
\noindent
{COMPANY\_HOOK --- what specifically excites you about this company's mission, product, or culture}. I am writing to express my interest in the \textbf{{POSITION}} position at {COMPANY\_NAME}. As a product-minded backend engineer with 3 years of experience building scalable systems and taking initiatives from idea to production, I am excited about the opportunity to contribute to your team.

\vspace{10pt}

%----------SECOND PARAGRAPH (VALUE & EXPERTISE)----------
% Highlight your product-minded approach and technical skills
\noindent
What sets me apart is my product-minded approach to engineering. I don't just write code---I focus on solving user problems and measuring impact. At Taager, I integrated e-commerce connectors that drove 300K+ orders, collaborated with the product team to improve confirmation rates, and served as a technical partner for top-tier merchants, building custom tooling to improve retention. Beyond my day-to-day work, I founded Yadwy, a multi-seller handmade marketplace, where I led product discovery, market research, and built the entire platform from scratch. I thrive on taking initiative and shipping solutions that create real value.

\vspace{10pt}

%----------THIRD PARAGRAPH (RELEVANT ACHIEVEMENT)----------
% TODO: Select the most relevant achievement from your CV for this role
% Options to choose from:
% - WooCommerce/Lightfunnels integration: 300K+ orders
% - E-commerce store builder: led team of 3, 100+ orders daily
% - Microservices optimization: 15% latency reduction, $500/month savings
% - Yadwy marketplace: full-stack founder experience
\noindent
{RELEVANT\_ACHIEVEMENT --- Choose the achievement from your experience that best aligns with the role. Include specific metrics and impact. For example: "At Taager, I built an e-commerce store builder platform from scratch, architecting the backend with Spring Boot and leading a team of 3 engineers to deliver an MVP now processing 100+ orders daily."}

\vspace{10pt}

%----------CLOSING PARAGRAPH----------
\noindent
I am genuinely excited about the opportunity to bring my skills in distributed systems, Spring Boot, and product-focused engineering to {COMPANY\_NAME}. I would welcome the chance to discuss how my experience building scalable backend systems and my initiative-taking mindset can contribute to your team's success.

\vspace{10pt}

\noindent
Thank you for considering my application. I look forward to hearing from you.

\vspace{20pt}

%----------SIGNATURE----------
\noindent
Sincerely,

\vspace{30pt}

\noindent
Hassan Refaat

%-------------------------------------------
\end{document}
